Appendix: Trends in age-adjusted mortality rates for blacks and whites by cause and sex, 1969-2013, United States

### 2017-03-10 Manuscript/Appendix-agestd-mort-rates.Rmd
cant remember

```{r plot-arrange-as-us-map, echo=F, fig.width=19.5, fig.height=14, results="asis", message = F}
roundUp <- function(x) 10^ceiling(log10(x))

# sex_i <- "Male"
# cod <- "Cardiovascular"

@@

    map.plot2 <- ggplot(data.sub2,
                        aes(y = rate.difference_mean, x = year)) +
      geom_vline(aes(xintercept = 1983), col = "#636363", lty = 3) +
      geom_vline(aes(xintercept = 1993), col = "#636363", lty = 3) +
      geom_ribbon(aes(ymin = rate.difference_LCL, ymax = rate.difference_UCL), fill = "grey", col = NA) +
      geom_line() +
      geom_hline(aes(yintercept = 0), col = "#636363") +
      scale_y_continuous(limits = c(0, lim.y)) + 
      facet_wrap( ~ state.reorder2, ncol = 11, drop = F, strip.position="bottom") +
      theme_classic(base_size = 20) +
      theme(axis.text.x = element_blank(),
            strip.background=element_blank(),
            axis.line=element_blank(),
            axis.ticks=element_blank()) +
      #theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      ylab("Black-white difference (per 100,000)") +
      xlab("Year (1969-2013)")

>>>>

```{r plot-arrange-as-us-map, echo=F, fig.width=19.5, fig.height=14, results="asis", message = F}
# sex_i <- "Male"
# cod <- "Cardiovascular"

@@

    map.plot2 <- ggplot(data.sub2,
                        aes(y = rate.difference_mean, x = year)) +
      geom_vline(aes(xintercept = 1983), col = "#636363", lty = 3) +
      geom_vline(aes(xintercept = 1993), col = "#636363", lty = 3) +
      geom_ribbon(aes(ymin = rate.difference_LCL, ymax = rate.difference_UCL), fill = "grey", col = NA) +
      geom_line() +
      geom_hline(aes(yintercept = 0), col = "#636363") +
      scale_y_continuous(limits = c(0, lim.y2)) + 
      facet_wrap( ~ state.reorder2, ncol = 11, drop = F, strip.position="bottom") +
      theme_classic(base_size = 20) +
      theme(axis.text.x = element_blank(),
            strip.background=element_blank(),
            axis.line=element_blank(),
            axis.ticks=element_blank()) +
      #theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      ylab("Black-white difference (per 100,000)") +
      xlab("Year (1969-2013)")
